{\normalsize Seminar: Formal Specification} \\[1ex] Security of Multithreaded Programs by Compilation\cite{Barthe07}

### 2012-01-22 paper/paper.tex
added defintion of tregion

>>>>

Now we can define $tregion$ according to a compilation function $\mathcal{C}$. I won't define
the compilation function here, because it is not that essential how it exactly looks like.

\begin{definition}{tregion}
$tregion(n)$ is defined as the set of instruction labels obtained by compiling the commands
$[c']^{n'}$ of the branching instruction $[c]^n$ of the source code with a compilation function $\mathcal{C}$.
\end{definition}
